---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# nwslR

<!-- badges: start -->
[[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) ![R-CMD-check](https://github.com/nwslR/nwslR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/nwslR/nwslR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`nwslR` is an R ecosystem that contains datasets and analysis functionality for the National Women’s Soccer League (NWSL). Founded in 2013, the NWSL is the United States’ top professional women’s soccer league, featuring players from all over the world.

Accessibility of data in women's sports (and particularly soccer) lags behind its male counterparts. This package is on contribution to a growing ecosystem of open data sources that aims to make data available to fans and analysts of the league. The main package, `nwslR`, provides functions to data easily access data that is loaded in the [nwsldata repo](https://github.com/nwslR/nwsldata). Data is updated several times a week during the season and more sporadically in the offseason. 

If you see anything you'd like added, changed, or updated, please open up a new issue of your own. If you are interested in contributing, please contact us directly. If you use this data in any work, please cite us. 

This package is currently in the process of changing and updating significantly, so it is suggested that you frequently update it so that you have access to the most recent version. CRAN submission will come when it reaches a stable state. 


## Installation

You can install the development version of nwslR from [GitHub](https://github.com/) with:

``` {r}
# install.packages("devtools")
devtools::install_github("nwslR/nwslR", 
                         ref = "adror1/build_first_draft")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(nwslR)
## basic example code
```

## Available Tables

- `load_player_match_stats()`: Loads player level stats for a given match
- `load_player_season_stats()`: Loads player level stats for a team/season
- `load_team_match_stats()`: Loads team level stats for a given match
- `load_team_season_stats()`: Loads team level stats for a team/season


# Example::
```{r}
#head(load_player_match_stats("angel-city-fc-vs-racing-louisville-fc-2022-09-25"))
```
```
